---
output: html_document
---

```{r global_options, include=FALSE}
knitr::opts_chunk$set(fig.width=9, fig.height=5, echo=FALSE,message=FALSE ,warnings=FALSE)
```

\newcommand{\R}{\mathbb{R}}
\newcommand{\N}{\mathcal{N}}
\newcommand{\TN}{\mathcal{TN}}
\newcommand{\boldU}{\mathbf{U}}
\newcommand{\boldUm}{\mathbf{U}^{(m)}}
\newcommand{\boldW}{\mathbf{W}}
\newcommand{\boldWm}{\mathbf{W}^{(m)}}
\newcommand{\boldV}{\mathbf{V}}
\newcommand{\boldX}{\mathbf{X}}
\newcommand{\boldQ}{\mathbf{Q}}
\newcommand{\boldI}{\mathbf{I}}
\newcommand{\boldH}{\mathbf{H}}
\newcommand{\boldHm}{\mathbf{H}^{(m)}}
\newcommand{\boldy}{\mathbf{y}}
\newcommand{\boldz}{\mathbf{z}}
\newcommand{\boldzero}{\mathbf{0}}
\newcommand{\boldone}{\mathbf{1}}

```{r}
source("helpers.R")
source("par_updates.R")
source("MLFS_mcmc.R")
source("MLFS.R")
source("par_updates.R")
source("rotation.R")
source("generate_data.R")

library(reshape2)
library(ggplot2)

source("experiment.R")

H = rbind(c(1, 1, 0, 0), 
          c(0, 0, 1, 1), 
          c(1, 0, 1, 0), 
          c(1, 0, 0, 1),
          c(0, 0, 0, 1), 
          c(1, 0, 0, 0))

set.seed(1)
R = nrow(H)
d = c(10, 10, 10, 10)
type = rep("gaussian", 4)


```

### Presence of subpopulations

Replace $\boldV_i \sim \N(\boldzero, \boldI)$ with  $\pi_1 \N(\boldone, \boldI) + \pi_2 \N(-\boldone, \boldI)$. Consider cases

- equal proportion of both subpopulations, $\pi_1 = 0.5$
- $\pi_1 = 0.25$

For visualisation of the 6 dimensional latent space, plot PC1 and PC2 and color according to the true class labels. 

#### Two subpopulations, $\pi_1 = 0.5$

```{r}
latent_data = generate_latent_subpopulations2(H, N = 300, d = d, gamma = 10, prop=0.5)
y = generate_y(latent_data$V, C = 2, continuous = FALSE)
X0 = generate_X(latent_data$U_list, type)
data = split_into_train_and_test(X0, y, prop=0.75)
MLFSobj = MLFS_mcmc(data$trainy, data$trainX, data$testy, data$testX, type, R, max_iter=1000, verbose=FALSE)

par(mfrow=c(1, 2))
plot(prcomp(latent_data$V[data$trainind, ])$x[, 1:2], col=data$trainy, pch=16, main="true (training data)")
plot(prcomp(MLFSobj$V_mean)$x[, 1:2], col=data$trainy, pch=16, main="multi-view output")

cat("test accuracy:", MLFSobj$pred_acc_test, "\n")
```

#### Two subpopulations, $\pi_1 = 0.25$

```{r}
latent_data = generate_latent_subpopulations2(H, N = 300, d = d, gamma = 10, prop=0.25)
y = generate_y(latent_data$V, C = 2, continuous = FALSE)
X0 = generate_X(latent_data$U_list, type)
data = split_into_train_and_test(X0, y, prop=0.75)
MLFSobj = MLFS_mcmc(data$trainy, data$trainX, data$testy, data$testX, type, R, max_iter=1000, verbose=FALSE, label_switching = FALSE)

par(mfrow=c(1, 2))
plot(prcomp(latent_data$V[data$trainind, ])$x[, 1:2], col=data$trainy, pch=16, main="true (training data)")
plot(prcomp(MLFSobj$V_mean)$x[, 1:2], col=data$trainy, pch=16, main="multi-view output")

cat("test accuracy:", MLFSobj$pred_acc_test, "\n")
```

#### Three subpopulations

```{r}
latent_data = generate_latent_subpopulations3(H, N = 300, d = d, gamma = 10, prop1=0.3, prop2=0.3)
y = generate_y(latent_data$V, C = 2, continuous = FALSE)
X0 = generate_X(latent_data$U_list, type)
data = split_into_train_and_test(X0, y, prop=0.75)
MLFSobj = MLFS_mcmc(data$trainy, data$trainX, data$testy, data$testX, type, R, max_iter=1000, verbose=FALSE)

par(mfrow=c(1, 2))
plot(prcomp(latent_data$V[data$trainind, ])$x[, 1:2], col=data$trainy, pch=16, main="true (training data)")
plot(prcomp(MLFSobj$V_mean)$x[, 1:2], col=data$trainy, pch=16, main="multi-view output")

cat("test accuracy:", MLFSobj$pred_acc_test, "\n")
```

### Two subpopulations with different betas

```{r}
set.seed(1234)
latent_data = generate_latent_subpopulations2_beta(H, N = 300, d = d, gamma = 10, prop=0.5)
y = latent_data$y
X0 = generate_X(latent_data$U_list, type)
data = split_into_train_and_test(X0, y, prop=0.75)
MLFSobj = MLFS_mcmc(data$trainy, data$trainX, data$testy, data$testX, type, R, max_iter=1000, verbose=FALSE)

par(mfrow=c(1, 2))
plot(prcomp(latent_data$V[data$trainind, ])$x[, 1:2], col=data$trainy, pch=16, main="true (training data)")
plot(prcomp(MLFSobj$V_mean)$x[, 1:2], col=data$trainy, pch=16, main="multi-view output")

cat("test accuracy:", MLFSobj$pred_acc_test, "\n")
```

