---
output: html_document
---

```{r global_options, include=FALSE}
knitr::opts_chunk$set(fig.width=10, fig.height=8, echo=FALSE,message=FALSE ,warnings=FALSE)
```

### Missing data

Hide $\{0\%, 25\%, 50\%, 75\%\}$ of the data in $\{1, 2, 3\}$ of the views. That is, 

- based on the values in the latent space, generate data for 4 gaussian views, each with 10 features, and the outcome y
- do for $\{1, 2, 3\}$ of the views
    - pick a view
    - choose randomly $\{0\%, 25\%, 50\%, 75\%\}$ of individuals and set their values in the current view to NA, both in training and test data
- observe accuracy on test data

Also see, what happens, if there are irrelevant features present. 

Consider two cases: binary classification, and univariate regression. 

```{r}
source("experiment.R")
H = rbind(c(1, 1, 1, 1), 
          c(0, 1, 1, 0), 
          c(1, 0, 0, 1), 
          c(0, 1, 0, 1), 
          c(1, 0, 1, 0), 
          c(0, 1, 0, 0))

set.seed(0)
R = nrow(H)
d = 5*c(10, 10, 10, 10)
type = rep("gaussian", 4)

# one view missing
prop_individuals = list(c(0.1, 0, 0, 0), 
                        c(0.25, 0, 0, 0), 
                        c(0.5, 0, 0, 0), 
                        c(0.75, 0, 0, 0))
res1 = experiment_missing_data(prop_individuals, H, d, type, R, max_iter = 3000, n_irrelevant_features = 0, test_only = FALSE, continuous = FALSE)

# two views missing
prop_individuals = list(c(0.1, 0.1, 0, 0), 
                        c(0.25, 0.25, 0, 0), 
                        c(0.5, 0.5, 0, 0), 
                        c(0.75, 0.75, 0, 0))
res2 = experiment_missing_data(prop_individuals, H, d, type, R, max_iter = 3000, n_irrelevant_features = 0, test_only = FALSE, continuous = FALSE)

# three views missing
prop_individuals = list(c(0.1, 0.1, 0.1, 0), 
                        c(0.25, 0.25, 0.25, 0), 
                        c(0.5, 0.5, 0.5, 0), 
                        c(0.75, 0.75, 0.75, 0))
res3 = experiment_missing_data(prop_individuals, H, d, type, R, max_iter = 3000, n_irrelevant_features = 0, test_only = FALSE, continuous = FALSE)

res = rbind(mutate(res1, n_views = 1), 
            mutate(res2, n_views = 2), 
            mutate(res3, n_views = 3)) %>%
  select(-train) %>%
  mutate(missing_pattern = factor(missing_pattern, labels = c(0.1, 0.25, 0.5, 0.75)))
names(res)[1:3] = c("multi-view imputation", "multi-view available cases", "logistic regression per view")
df.m = melt(res, id.vars = c("missing_pattern", "n_views"))

ggplot(df.m) + 
  geom_boxplot(aes(missing_pattern, value, col=variable)) + 
  theme_bw() + scale_color_brewer("Multi-view method", palette = "Set1") + 
  facet_wrap(~ n_views) + 
  ylim(0, 1) + 
  xlab("Proportion of individuals with NA") + 
  ylab("Prediction accuracy (test data)") + 
  theme(axis.text.x = element_text(angle = 45, hjust = 1))  


```