---
output: html_document
---

```{r global_options, include=FALSE}
knitr::opts_chunk$set(fig.width=9, fig.height=9, echo=FALSE,message=FALSE ,warnings=FALSE)
```

```{r}
source("helpers.R")
source("par_updates.R")
source("MLFS_mcmc.R")
source("MLFS.R")
source("par_updates.R")
source("rotation.R")
source("generate_data.R")

library(reshape2)
library(ggplot2)
library(gridExtra)
source("https://raw.githubusercontent.com/briatte/ggcorr/master/ggcorr.R")

```

### Exploring structure in the latent space

What we would expect: The larger $N$ is, the more structure we will have in the latent space. 

To explore the behavior w.r.t. $N$, I generated data for $N \in \{25, 50, 100, 250\}$ training data points, where there was some correlation between the true latent variables. Here is the correlation matrix:

```{r, fig.width=4, fig.height=4}
Sigma = diag(6)
Sigma[1, 3] <- Sigma[3, 1] <- 0.7
Sigma[1, 5] <- Sigma[5, 1] <- -0.7
Sigma[2, 4] <- Sigma[4, 2] <- 0.5
rownames(Sigma) <- colnames(Sigma) <- paste0("V", 1:6)
ggcorr(data=NULL, cor_matrix = Sigma, low = "steelblue", mid = "white", high = "darkred") + ggtitle(sprintf("True correlation matrix"))
```


Now I picked out one sample (from the mcmc trace) of $\Sigma_V$ and converted this to a correlation matrix. 


```{r, eval=FALSE}
set.seed(1)

H = rbind(c(1, 1, 0, 0), 
          c(0, 0, 1, 1), 
          c(1, 0, 1, 0), 
          c(1, 0, 0, 1),
          c(0, 0, 0, 1), 
          c(0, 1, 0, 0))

R = nrow(H)
d = 5*c(10, 10, 10, 10)
type = rep("gaussian", length(d))
p_list = list()
n_values = c(25, 50, 100, 250)
for(i in 1:length(n_values)){
  latent_data = generate_latent_subspace_corstruct(H, N = 2*n_values[i], Sigma, d = d, gamma = 10)
  y = generate_y(latent_data$V, C = 2, continuous = FALSE)
  X0 = generate_X(latent_data$U_list, type)
  data = split_into_train_and_test(X0, y, prop=0.5)
  MLFSobj = MLFS_mcmc(data$trainy, data$trainX, data$testy, data$testX, type, R, max_iter=2000, verbose=TRUE, label_switching = FALSE)
  cormat = cov2cor(MLFSobj$sigma_V)
  print(cormat)
  rownames(cormat) <- colnames(cormat) <- paste0("V", 1:R)
  p = ggcorr(data=NULL, cor_matrix = cormat, low = "steelblue", mid = "white", high = "darkred") + ggtitle(sprintf("Correlation structure in the latent space for N = %d", n_values[i]))
  p_list[[i]] = p
}
save(p_list, file="temp_corstruct.RData")
```

```{r}
load("temp_corstruct.RData")
do.call("grid.arrange", p_list)
```

